# Problemset Example

Example of an RTutor interactive Problemset

#### Author:  Sebastian Kranz

Adapt the working directory below and press Ctrl-Alt-R (run all chunks). This creates the problem set files and the sample solution from this solution file.

#< ignore
```{r "create_ps",include=TRUE , eval=TRUE}
library(restorepoint)
# facilitates error detection
set.restore.point.options(display.restore.point=!TRUE)

library(RTutor)
#library(restorepoint)
setwd("D:/libraries/RTutor/examples")
ps.name = "Example"; sol.file = paste0(ps.name,"_sol.Rmd")
libs = c() # character vector of all packages you load in the problem set
#name.rmd.chunks(sol.file) # set auto chunk names in this file

create.ps(sol.file=sol.file, ps.name=ps.name, user.name=NULL,libs=libs, stop.when.finished=FALSE)

show.ps(ps.name, user.name="Seb", load.sav=!TRUE,  sample.solution=FALSE, run.solved=!TRUE, catch.errors=TRUE, launch.browser=!TRUE, make.session.ps=TRUE)

stop.without.error()
```
#>

## Exercise 1 -- Summary statistics

a) First part

Compute 1+1+1 and store it in z
```{r "1 a)"}
#< compute z

## First store the intermediate result 1+1 in a variable 'y'
y = 1+1

## Now compute z by adding 1 to y
z = y+1
#>
```


b)
We often want to compute some summary statistic of a vector.
For example:


```{r "1 b) 1",fig.height=3}
#< task
x = 10:20
# Computing the sum of x
sum(x)
#>
```

Now compute the mean of x.
```{r "1 b) 2"}
mean(x)
#< hint
cat("There already exist R functions for many things. To find them use Google, e.g. search for 'R compute mean'.")
#>
```


#< info "useful functions for numeric vectors"
Here are examples for useful R functions
```{r "1 "}
max(c(1,5,2)) # returns maximum
min(c(1,5,2)) # returns minimum

sum(c(1,5,2,NA), na.rm=TRUE) # returns sum of all numbers, ignore NA
cumsum(c(1,5,2)) # returns cummulated sum
diff(c(1,5,2)) # returns the vector of differences
```
#>


#< award "mean means mean"
Well, in some occasions one can just guess the name of an R function. The function to compute the mean of a vector, or matrix is called 'mean'. Usually, it is much quicker to goggle than to guess function names, however.
#>

## Exercise 2 -- Computing with vectors
```{r "2 "}
#< settings
import.var = c("x")
#>
```
a) Let y be a vector that contains the squared elements of x. Show y
```{r "2 a)"}
y = x^2
y
```

b) Run this chunk and check out the data button
```{r}
#< task_notest
# Generating a data frame
df = data.frame(a=c(1,1,2,2,2,3,3,4), b = runif(8), c="Hi")
df
#>
```

That's all folks!