# Problemset Example

  
```{r include=FALSE}

ps.dir =  'D:/libraries/RTutor/examples' # set to the folder in which this file is stored
ps.file = 'Example.Rmd' # set to the name of this file
user.name = '' # set to your user name

library(RTutor)
check.problem.set('Example', ps.dir, ps.file, user.name=user.name, reset=FALSE)

# To check your solution in RStudio save (Ctrl-S) and then run all chunks (Ctrl-Alt-R)
```
Name: `r user.name`


Example of an RTutor interactive Problemset

#### Author:  Sebastian Kranz

Adapt the working directory below and press Ctrl-Alt-R (run all chunks). This creates the problem set files and the sample solution from this solution file.


## Exercise 1 -- Summary statistics

a) First part

Compute 1+1+1 and store it in z
```{r "1 a)", optional = TRUE}

```


b)
We often want to compute some summary statistic of a vector.
For example:


```{r "1 b) 1",fig.height=3}
x = 10:20
# Computing the sum of x
sum(x)
```

Now compute the mean of x.
```{r "1 b) 2"}

```


info("useful functions for numeric vectors") # Run this line (Strg-Enter) to show info



## Exercise 2 -- Computing with vectors
a) Let y be a vector that contains the squared elements of x. Show y
```{r "2 a)"}

```

b) Run this chunk and check out the data button
```{r "2 b)"}
# Generating a data frame
df = data.frame(a=c(1,1,2,2,2,3,3,4), b = runif(8), c="Hi")
df
```

That's all folks!
